Spin canonical divisors of log stacky curves

### 2015-06-19 stacky_write_up/spin_cring.tex

In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. This is proven in Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather involved induction. In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.

>>>>

In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. This is proven in Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather involved induction. In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.
